Contracts for unions and intersections are hard for Nickel

### 2021-05-11 paper.tex
Add lstlisting basic configuration

@@

\begin{figure}
  \begin{center}
    \begin{lstlisting}
        { tag: <Integer, String>, value: Dyn }
    \end{lstlisting}
  \end{center}
\caption{Encoding of the union type: integer or a string}
\label{fig:union-encoding}
\medskip
\small
In Nickel, \lstinline+<A, B, C>+ is the type of a C-like enumeration that can
take value \lstinline+A+, \lstinline+B+ or \lstinline+C+, while \lstinline+Dyn+
is the dynamic unitype.
\end{figure}

@@

\begin{lstlisting}
type either = Left of int | Right of string
\end{lstlisting}

\begin{lstlisting}
{ tag : <Left>, val : Num} | { tag : <Right>, val : Str}
\end{lstlisting}

>>>>

%%%%%%%%%%% LST listing confinguraiton %%%%%%%%%%%

\lstdefinelanguage{nickel}{
    keywords=[1]{
      if,
      then,
      else,
      switch,
    },
    keywords=[2]{
      let,
      rec,
      fun,
      in
    },
    keywords=[3]{
      Num,
      Bool,
      Str,
      List,
      Dyn,
      forall,
    },
    keywords=[4]{
      true,
      false,
      null
    },
    keywords=[5]{
      doc,
      default,
    },
    sensitive=true, % keywords are case-sensitive
    morecomment=[l]{//}, % l is for line comment
    morecomment=**[is][\color{dark-grey}]{\$}{\$},
    morestring=[b]", % defines that strings are enclosed in double quotes
    morestring=[s]{m\#"}{"\#m},
    moredelim=[is][\color{bright-grey}]{\$}{\$},
    literate=
        *{->}{$\rightarrow$}1
        {=>}{$\Rightarrow$}1
        {>=}{$\geq$}1
        {<=}{$\leq$}1
} %

\lstset{
  language={nickel},
  basicstyle=\small\ttfamily, % Global Code Style
  captionpos=b, % Position of the Caption (t for top, b for bottom)
  extendedchars=true, % Allows 256 instead of 128 ASCII characters
  tabsize=2, % number of spaces indented when discovering a tab
  columns=fixed, % make all characters equal width
  keepspaces=true, % does not ignore spaces to fit width, convert tabs to spaces
  showstringspaces=false, % lets spaces in strings appear as real spaces
  breaklines=true, % wrap lines if they don't fit
  frame=trbl, % draw a frame at the top, right, left and bottom of the listing
  frameround=tttt, % make the frame round at all four corners
  framesep=4pt, % quarter circle size of the round corners
  numbers=left, % show line numbers at the left
  numberstyle=\tiny\ttfamily, % style of the line numbers
  % commentstyle=\color{dark-grey}, % style of comments
  % keywordstyle=[1]\color{blue-portage}, % style of keywords
  % keywordstyle=[2]\color{orange-vivid-tangerine}, % style of keywords
  % keywordstyle=[3]\color{blue-portage}, % style of keywords
  % keywordstyle=[4]\color{green-pea}, % style of keywords
  % keywordstyle=[5]\color{pink-froly}, % style of keywords
  % stringstyle=\color{blue-marguerite}, % style of strings
}

@@

\begin{figure}
  \begin{center}
\begin{lstlisting}[language=nickel]
{tag: <Num, Str>, value: Dyn}
\end{lstlisting}
  \end{center}
\caption{Encoding of the union type: integer or a string}
\label{fig:union-encoding}
\medskip
\small
In Nickel, \lstinline+<A, B, C>+ is the type of a C-like enumeration that can
take value \lstinline+A+, \lstinline+B+ or \lstinline+C+, while \lstinline+Dyn+
is the dynamic unitype.
\end{figure}

@@

\begin{lstlisting}[language=caml]
type either = Left of int | Right of string
\end{lstlisting}

\begin{lstlisting}[language=nickel]
{ tag : <Left>, val : Num} | { tag : <Right>, val : Str}
\end{lstlisting}
